---
title: "Analyzing How Result of the 2019 Canadian Federal Election is Affected"
author: "Shuxian Cao"
date: "22 December 2020"
output:
  bookdown::pdf_document2:
    latex_engine: lualatex
notice: "@*"
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(tidyverse)
library(dplyr)
library(knitr)
library(table1)
library(ggplot2)
library(ggpubr)

# Loading in the cleaned survey Data
election_survey <- read_csv("election_data.csv")

# Loading in the cleaned census Data
gss_census <- read_csv("gss.csv")
```

# Information

**Topic:** Analyzing How Result of the 2019 Canadian Federal Election is Affected

**Author:** Shuxian Cao

**Date:** December 22, 2020

**Code and data supporting this analysis is available at:**

https://github.com/Susan-csx/Analyzing-How-Result-of-the-2019-Canadian-Federal-Election-is-Affected.git

# Abstract

The 2019 Canadian Federal Election turns out that the Liberal Party eventually won a minority government with less seats in the Cabinet as well as a lower percentage of vote share than its strongest competitor (‘Party standing’, 2019), the Conservative Party. This paper will be observing how the election results will be affected by the differences among voters, with a target population based on the entire Canadian population. In addition, a prediction on proportion of the potential Liberal Party voters will also be made based on their vote intentions, birthplace, age groups and education levels. In order to start the analysis, an election data set obtained by the 2019 Canadian Election Survey (CES) (Stephenson, Harell, Rubenson & Loewen, 2020) and a census data set from 2013 Canadian General Social Surveys (GSS) (Statistics Canada, 2013) are selected for building a logistic regression model. The result shows that the Liberal Party might not win the 2019 Canadian Federal Election if "everyone" in Canada votes due to the low estimated proportion of voting the Liberals.

# Keywords

Observational Study, Post Stratification, Step-wise Selection, 2019 Canadian Election, Liberal Party, Education

# Introduction

In the past 2019 Canadian Federal Election, the Liberal Party, which is led by Prime Minister Justin Trudeau, eventually resulted in a minority government instead of the majority one (Clarke & Levett, 2019) due to the lost of 20 seats in the Cabinet, while its strongest competitor, the Conservative party, gained 26 more seats than the 2015 election for its official opposition (Cecco, 2019). Despite the decreasing pattern in the Cabinet, the Liberal Party also lost the Canadian General Public significantly during the recent election (Clarke & Levett, 2019), ending up with 33.1% in vote share (‘Party standing’, 2019). The Conservative party, on the other hand, had 34.4% supporters throughout Canada (‘Party standing’, 2019). It is worth noting that although what the Liberals and the Conservatives claimed on their platforms seemed to be interchangeable (Urback, 2019), the plans they announced (for example, the welcome towards Syrian refugees) (Cecco, 2019) meant differently to the individual citizens. Hence, the question of whether the result of the 2019 Canadian Federal Election will change if the general public is now allowed to directly vote for the party they support is raised for further analysis. This paper analyzed the factors that might influence the result of the 2019 election based on a hypothesis that there would be a difference if "everyone" votes for the election.

In order to form a better prediction on the proportion of Liberal voters if "everyone" in Canada votes, a post-stratification analysis is provided, allowing people to be more confident "in the validity of our inferences about population parameters of interest" (Barboza & Williams, 2005). To be more specific, since both raw data sets from CES and GSS given for the analysis are unstratified, post-stratification analysis can be used to obtain more significant estimators (Thompson & Wu, 2015).

This paper analyzed how the results of the 2019 Canadian Federal Election will be affected based on two data sets from either CES or GSS. Both data sets themselves, post-stratification method applied on the GSS census data as well as the model used for predicting the potential proportion of Liberal voters will be discussed in the Methodology section (Section 5). Graphs and tables will be presented in the Results Section (Section 6) for visualizing the relationship between vote choices and the voters' birthplace, age groups and education level, while the actual meaning of results and the further improvement on this study will be provided in the Discussion Section (Section 7). For the last section, there are references for a more detailed check.

# Methodology

## Data

To analyze how the results of the 2019 Canadian Federal Election will be influenced, two data sets are retrieved from either the 2019 Canadian Election Survey (CES) or the 2013 General Social Survey (GSS) which is held by Statistics Canada.

The data set from 2019 CES is a raw online survey data set which is grouped by region and aims for a balance on gender and age (Stephenson, Harell & two authors, 2020). Thus, data cleaning is applied before the actual study. After selecting several interesting variables from the original raw data set, the missing values "NA" in the observations are removed. Then, a new column of the response variable `vote_liberal` is reated for a categorization from strings of words to 0 and 1. Mutations on other variables are also provided for a further match between the CES data set and the GSS data set, forming a final survey data set called `election_survey` with 24580 observations and 7 variables. 

Also, baseline characteristics of the `election_survey` data are provided in Table \@ref(tab:table2) (Results Section), showing the percentages that each level occupies in a variable. For example, the variable `Bornin_Canada` includes 21357 (86.9%) people who were born in Canada, and 3223 (13.1%) otherwise. What shall be concerned is that for the variable `Likely_to_Vote` (vote intention), almost three quarters of respondents claims that they are certain to vote in the 2019 Canadian Federal Election.

For the data set from 2013 GSS, data cleaning is performed by first removing all the missing values "NA" as well. A matching check is needed since the post-stratification method requires the names of both variables and levels within each variables to be the same. For the final GSS data set `gss_census`, targeting all people that are 15 years of age and older in Canada (Burns, 2015), 2522 observations and 7 variables are included.

Hence, `Sex`, `Income`, `Age`, `Education`, `Likely_to_Vote` and `Bornin_Canada` are the six variables selected for analyzing the likelihood of the Liberal Party winning the 2019 Canadian Federal Election, while `vote_liberal` in the `election_survey` data set is the response variable.

## Model

Compared to the multiple linear regression which is used for numeric prediction, multiple logistic regression with post-stratification is chosen for modeling the likelihood of the Liberal Party winning the 2019 Canadian Federal Election based on the 2019 CES data set since the response variable is binary. That is to say, `vote_liberal` is a discrete binary response variable that will be equal to 1 if the respondent votes for the Liberal Party and 0 otherwise. Moreover, the post-stratification analysis helps to obtain more significant estimators (Thompson & Wu, 2015) by stratifying observations into different groups. 

To satisfy the requirement of a parsimonious model (Chen, Hu & Yang, n.d.), the analysis starts with a `full_model` with all five explanatory variables from the election survey data set (CES), providing an AIC value of 26058.46. After applying the backward elimination selection with AIC, the AIC value of the `final_model` is 26044.41 (Table \@ref(tab:table1)). According to Bevan's introduction on Akaike information criterion, the lower the AIC, the better the model fits (Bevans, 2020). Thus, two categorical variables `Income` and `Sex` are removed from five initial predictor variables, `Likely_to_Vote`, `Bornin_Canada`, `Education`, `Age`, `Income` and `Sex` which match the ones in the 2013 GSS census data set. 

The final multiple logistic regression model, which is run by R, is shown below:
$$
log(\frac{p}{1-p}) = \beta_0 + \beta_1 X_{1_{likelyvote}} + \beta_2 X_{2_{Unlikelyvote}} + \beta_3 X_{3_{notvote}} + \beta_4 X_{4_{BornCA}} + \beta_5 X_{5_{belowhigh}} + \beta_6 X_{6_{postsecond}}
$$
$$
+ \beta_7 X_{7_{University}} + \beta_8 X_{8_{Age25to34}} + \beta_9 X_{9_{Age35to44}} + \beta_{10} X_{10_{Age45to54}} + \beta_{11} X_{11_{Age55to64}} + \beta_{12} X_{12_{Age65to74}} + \beta_{13} X_{13_{Age75above}} + \epsilon,
$$

where the log odds ration formula $log(\frac{p}{1-p})$ on the left-hand side is formed by $log$ (natural logarithm), $p$ (proportion of voting the Liberal Party in 2019 Canadian Federal Election) and $\frac{1}{1-p}$ (the "odd ratio") form a notation: $log(\frac{p}{1-p})$. On the right-hand side, $\beta_0$ is the intercept term when all the predictor variables $X_i = 0$ (for i from 1 to 13), while each $X_i$ above is an explanatory dummy variable in the final logistic regression model. That is to say, all the predictor variables are categorical, which take a value of 0 or 1. Moreover, each corresponding $\beta_i$ for i = 1,...,13 are the mean difference in the log odds ratio between $X_i = 0$ and $X_i = 1$, while keeping all the other predictors fixed. For example, $\beta_1$ indicates the average difference of voters' intention in the log odds ratio between "likely to vote" and other intention like "unlikely to vote. At last, $\epsilon$ represents the error term of the model.

\newpage

# Results

&nbsp;

```{r Fit Model, include = FALSE}
# Model With all variables
full_model <- glm(vote_liberal ~ Likely_to_Vote + Bornin_Canada + Education + Age + Income + Sex, data = election_survey, family =  "binomial")

# Backward Elimination with AIC
step(full_model, direction = "backward")

# Model with Likely_to_Vote, Bornin_Canada, Education and Age (AIC 26044)
final_model <- glm(vote_liberal ~ Likely_to_Vote + Bornin_Canada + Education + Age, data = election_survey, family =  "binomial")

# Summary Table for the Final Model
summary(final_model)
```

```{r table1}
# Visualize AIC
model_name <- c("full_model", "final_model")
aic_value <- c(26058.46, 26044.41)
aic_table <- data.frame(model_name, aic_value)
kable(aic_table, align = "c", format = "markdown", col.names = c("**Model**", "**AIC**"),
      caption = "Summary - AIC Score of Potential Models")
```

After building a logistic regression model `full_model` with all variables from the `election_survey` data set, a backward elimination with AIC (Chee, 2020) is applied to the `full_model` in order to find a parsimonious model. To be more specific, the AIC of the `final_model` which includes four variables: Likely_to_Vote, Bornin_Canada, Education and Age, drops from 26058 to 26044 by the elimination in Table \@ref(tab:table1).

&nbsp;

```{r, include = FALSE}
# Baseline Characteristic
table1(~Likely_to_Vote + Bornin_Canada + Education + Age, data = election_survey)
```

```{r table2}
predictor <- c("**Likely_to_Vote**", "Certain to vote", "Likely to vote", "Unlikely to vote", "Will not vote", "**Bornin_Canada**", "No", "Yes", "**Education**", "Above High", "Below High", "Post-secondary", "University", "**Age**", "15 to 24", "25 to 34", "35 to 44", "45 to 54", "55 to 64", "65 to 74", "75 and above")
value <- c(" ", "18269 (74.3%)", "3342 (13.6%)", "1060 (4.3%)", "1909 (7.8%)", " ", "3223 (13.1%)", "21357 (86.9%)", " ", "8730 (35.5%)", "1152 (4.7%)", "5273 (21.5%)", "	9425 (38.3%)", " ", "1168 (4.8%)", "4141 (16.8%)", "4442 (18.1%)", "4237 (17.2%)", "5159 (21.0%)", "4295 (17.5%)", "1138 (4.6%)")
baseline_table <- data.frame(predictor, value)
kable(baseline_table, align = "c", format = "markdown", col.names = c(" ", "**Overall (N=24580)**"),
      caption = "Baseline Characteristics of the data")
```

Table \@ref(tab:table2) above displays baseline characteristics of the `election_survey` data set from 2019 CES. Among a number of 24580 participants, 74.3% of them claims that they are certain to vote for the 2019 Canadian Federal Election. For the birthplace of voters, 86.9% of the respondents were born in Canada. Also, 73.8% of the respondents performs an education level that is above high school (including high school graduates, bachelors, masters and even doctors). Among the seven age groups, the youngest and the oldest age groups performs the lowest participation rate, compared to other groups which are mostly equal.

\newpage

```{r table3}
# Visualize the Summary Table
kable(broom::tidy(final_model), align = "c", format = "markdown", digits = 3,
      col.names = c("**Term**", "**Estimate**", "**Std. Error**", "**Test Statistic**", "**P-Value**"),
      caption = "Summary - the Final Election Logistic Regression Model")
```

Additionally, Table \@ref(tab:table3) summarizes the estimated values of intercept $\hat{\beta_0}$ and slopes $\hat{\beta_i}$ (for i = 1,...,13) as well as standard errors, test statistics and p-values for the `final_model`, which is chosen to predict the proportion of Liberal voters in the past 2019 Canadian Federal Election. Thus, the fitted logistic model is shown below.

$$
log(\frac{\hat{p}}{1-\hat{p}}) = -0.829 - 0.050 X_{1_{likelyvote}} - 16.596 X_{2_{Unlikelyvote}} - 16.737 X_{3_{notvote}} - 0.230 X_{4_{BornCA}}
$$
$$
 - 0.272 X_{5_{belowhigh}} - 0.025 X_{6_{postsecond}} + 0.442 X_{7_{University}} - 0.086 X_{8_{Age25to34}} - 0.028 X_{9_{Age35to44}}
$$
$$
 - 0.047 X_{10_{Age45to54}} +  0.034 X_{11_{Age55to64}} + 0.144 X_{12_{Age65to74}} + 0.146 X_{13_{Age75above}},
$$

```{r table4}
estimation_in_logodds <- final_model %>%
  predict(newdata = gss_census)

estimation <- exp(estimation_in_logodds)/(1+exp(estimation_in_logodds))

predicted_prop_by_post <- gss_census %>%
  mutate(predicted_prop = estimation*n) %>%
  summarise(predict = sum(predicted_prop)/sum(n))

kable(predicted_prop_by_post, format = "markdown", digits = 3, align = "c", col.names = "**predict**",
      caption = "The Predicted Proportion of Voters for Liberal Party")
```

Based on the 2019 Canadian Election Survey (CES) (Stephenson, Harell, Rubenson & Loewen, 2020) and the 2013 Canadian General Social Surveys (GSS) (Statistics Canada, 2013), ${\hat{y}}^{PS} = \frac{\sum{N_j{\hat{y}_j}}}{\sum{N_j}}$ (Caetano, 2020) can be used for calculating the predicted proportion of voters for the Liberal Party, which results in an estimation of **0.269** in Table \@ref(tab:table4) below. That is to say, 26.9% of people are estimated to vote for the Liberal Party after the post-stratification analysis of the proportion of Liberal Party voters modeled by a logistic regression model, which accounted for `Likely_to_Vote`, `Bornin_Canada`, `Education` and `Age`.

\newpage

```{r, include = FALSE}
vote0_born <- election_survey %>%
  filter(vote_liberal == 0) %>%
  group_by(Bornin_Canada) %>%
  summarise(counts = n(), .groups = 'drop') %>%
  mutate(prop_vote = round(counts/sum(counts), 4))

vote1_born <- election_survey %>%
  filter(vote_liberal == 1) %>%
  group_by(Bornin_Canada) %>%
  summarise(counts = n(), .groups = 'drop') %>%
  mutate(prop_vote = round(counts/sum(counts), 4))

vote0_born_pie <- ggplot(vote0_born, aes(x = "", y = prop_vote, fill = Bornin_Canada)) +
  geom_bar(width = 1, stat = "identity", color = "white") +
  coord_polar("y", start = 0) +
  theme_void() +  
  labs(title = "If Born in Canada when vote_liberal = 0") +
  scale_fill_brewer(palette="PuBu")

vote1_born_pie <- ggplot(vote1_born, aes(x = "", y = prop_vote, fill = Bornin_Canada)) +
  geom_bar(width = 1, stat = "identity", color = "white") +
  coord_polar("y", start = 0) +
  theme_void() +  
  labs(title = "If Born in Canada when vote_liberal = 1") +
  scale_fill_brewer(palette="PuBu")
```

```{r, include = FALSE}
vote0_age <- election_survey %>%
  filter(vote_liberal == 0) %>%
  group_by(Age) %>%
  summarise(counts = n(), .groups = 'drop') %>%
  mutate(prop_vote = round(counts/sum(counts), 4))

vote1_age <- election_survey %>%
  filter(vote_liberal == 1) %>%
  group_by(Age) %>%
  summarise(counts = n(), .groups = 'drop') %>%
  mutate(prop_vote = round(counts/sum(counts), 4))

vote0_age_pie <- ggplot(vote0_age, aes(x = "", y = prop_vote, fill = Age)) +
  geom_bar(width = 1, stat = "identity", color = "white") +
  coord_polar("y", start = 0) +
  theme_void() +  
  labs(title = "Age Group when vote_liberal = 0") +
  scale_fill_brewer(palette="PuBu")

vote1_age_pie <- ggplot(vote1_age, aes(x = "", y = prop_vote, fill = Age)) +
  geom_bar(width = 1, stat = "identity", color = "white") +
  coord_polar("y", start = 0) +
  theme_void() +  
  labs(title = "Age Group when vote_liberal = 1") +
  scale_fill_brewer(palette="PuBu")
```

```{r, include = FALSE}
vote0_edu <- election_survey %>%
  filter(vote_liberal == 0) %>%
  group_by(Education) %>%
  summarise(counts = n(), .groups = 'drop') %>%
  mutate(prop_vote = round(counts/sum(counts), 4))

vote1_edu <- election_survey %>%
  filter(vote_liberal == 1) %>%
  group_by(Education) %>%
  summarise(counts = n(), .groups = 'drop') %>%
  mutate(prop_vote = round(counts/sum(counts), 4))

vote0_edu_pie <- ggplot(vote0_edu, aes(x = "", y = prop_vote, fill = Education)) +
  geom_bar(width = 1, stat = "identity", color = "white") +
  coord_polar("y", start = 0) +
  theme_void() +  
  labs(title = "Education Level when vote_liberal = 0") +
  scale_fill_brewer(palette="PuBu")

vote1_edu_pie <- ggplot(vote1_edu, aes(x = "", y = prop_vote, fill = Education)) +
  geom_bar(width = 1, stat = "identity", color = "white") +
  coord_polar("y", start = 0) +
  theme_void() +  
  labs(title = "Education Level when vote_liberal = 1") +
  scale_fill_brewer(palette="PuBu")
```

```{r}
ggarrange(vote0_born_pie, vote1_born_pie, vote0_age_pie, vote1_age_pie, ncol = 2, nrow = 2)
```

```{r fig1, fig.cap = "How Birthplace, Education Level and Age Groups Affect the Voters’ Choice of Liberal Party"}
ggarrange(vote0_edu_pie, vote1_edu_pie)
```

Six Pie-charts in Figure \@ref(fig:fig1) depict patterns of how voters' birthplace, age groups, and education levels might influence the voters' choice of Liberal Party, using the explanatory variables of the logistic regression `final_model`: `Bornin_Canada`, `Age` and `Education`.

\newpage

# Discussion

## Summary



## Conclusions



## Weaknesses



## Next Steps



# References

## Data Sets & User's Guide

General social survey on Social Identity (cycle 27), 2013. (2013).  In Statistics Canada. Retrieved 

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; December 5, 2020 from https://sda-artsci-utoronto-ca.myaccess.library.utoronto.ca/

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; cgi-bin/sda/hsda?harcsda4+gss27v2.

Burns, M. (2015). General Social Survey Cycle 27: Social Identity Public Use Microdata File 

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; Documentation and User’s Guide. In Statistics Canada. Retrieved  December 5, 2020 from

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; https://sda-artsci-utoronto-ca.myaccess.library.utoronto.ca/sdaweb/dli2/gss/gss27v2/more_doc/

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; GSS27ENgidV2.pdf.

Stephenson, L.B., Harell, A., Rubenson, D. & Loewen, P.J. (2020). 2019 Canadian Election Study - 

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; Online Survey. https://doi.org/10.7910/DVN/DUS88V, Harvard Dataverse, V1.

Stephenson, L.B., Harell, A., Rubenson, D. & Loewen, P.J. (2020). The 2019 Canadian Election Study 

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; – Online Collection. [dataset].

## Other References

Allaire, J.J., Grolemund, G. & Xie, Y.H. (2018). R Markdown: The Definitive Guide. Boca Raton,

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; Florida: Chapman; Hall/CRC. Retrieved December 5, 2020 from https://bookdown.org/

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; yihui/rmarkdown.

Allaire, J.J., Atkins, A., Cheng, J., Chang, W., Iannone, R., Luraschi, J., McPherson, J.,

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;  Ushey, K., Wickham, H. & Xie, Y.H. (2020). Rmarkdown: Dynamic Documents for r. 

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;  Retrieved December 5, 2020 from https://github.com/rstudio/rmarkdown.

Barboza, I. & Williams R. (2005). Post-stratification and Response Bias in Survey Data with Applications

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; in Political Science. In Michigan State University. Retrieved December 10, 2020 from

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; https://msu.edu/~barbozag/Web/poststrat.pdf.

Bevans, R. (2020). An introduction to the Akaike information criterion. In Scribber. Retrieved 

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; December 10, 2020 from https://www.scribbr.com/statistics/akaike-information-criterion/.

Cecco, L. (2019). Canada elections: Trudeau wins narrow victory to form minority government. In The 

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; Guardian. Retrieved December 5, 2020 from https://www.theguardian.com/world/2019/oct/22/

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; canada-elections-justin-trudeau-wins-narrow-victory-to-form-minority-government.

Clarke, S. & Levett, C. (2019). Canada election 2019: full results. In The Guardian. Retrieved December 5,

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; 2020 from https://www.theguardian.com/world/2019/oct/22/canada-election-2019-full-results.

Caetano, S.J. (2020). STA304: Multilevel Regression & Poststratification. Pg.4.

Chee, S.S. (2020). STA302H1F/1001HF Autumn 2020 Assignment # 3. Pg.3.

Chen, H.W., Hu, X. & Yang, Z.C. (n.d.). Model Selection for Linear Regression Model. Retrieved 

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; December 10, 2020 from https://jbhender.github.io/Stats506/F17/Projects/Group21_Model

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; _Selection.html.

François, R., Henry, L., Müller, K. & Wickham, H. (2020). dplyr: A Grammar of Data 

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; Manipulation. R package version 1.0.2. Retrieved December 10, 2020 from 

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; https://CRAN.R-project.org/package=dplyr.

Horn, B. (2013). RColorBrewer Palettes. In Applied R Code. Retrieved December 16, 

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; 2020 from http://applied-r.com/rcolorbrewer-palettes/.

Kassambara. (2017). Ggplot2 - Easy Way to Mix Multiple Graphs on The Same Page. In Sthda. 

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; Retrieved December 16, 2020 from http://www.sthda.com/english/articles/24-ggpubr-

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; publication-ready-plots/81-ggplot2-easy-way-to-mix-multiple-graphs-on-the-same-page/.

Kassambara. (2017). Plot One Variable: Frequency Graph, Density Distribution and More. In Sthda. 

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; Retrieved December 16, 2020 from http://www.sthda.com/english/articles/32-r-graphics-

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; essentials/133-plot-one-variable-frequency-graph-density-distribution-and-more/.

Kassambara, A. (2020). ggpubr: 'ggplot2' Based Publication Ready Plots. R package version 0.4.0.

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; https://CRAN.R-project.org/package=ggpubr.

Party standings. (2019). In CBC News. Retrieved December 5, 2020 from https://newsinteractives.cbc.ca/

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; elections/federal/2019/results/.

Rich, B. (2020). table1: Tables of Descriptive Statistics in HTML. R package version 1.2.1. Retrieved 

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; December 5, 2020 from https://CRAN.R-project.org/package=table1.

R Core Team (2020). R: A language and environment for statistical computing. R Foundation for Statistical

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; Computing, Vienna, Austria. URL https://www.R-project.org/.

Thompson, M. & Wu, C.B. (2015). ICSA Book Series in Statistics: Sampling Theory and Practice. 

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; ISBN 978-3-030-44246-0. Pg. 38.

Urback, R. (2019). What's the difference between the Conservative and Liberal platforms? The colour: 

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; Robyn Urback. In CBC News.  Retrieved December 5, 2020 from https://www.cbc.ca/

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; news/opinion/policy-platforms-1.5298859.

Wickham, H. (2016). ggplot2: Elegant Graphics for Data Analysis. Springer-Verlag New York.

Wickham, H. (2019). Welcome to the tidyverse. Journal of Open Source Software, 4(43), 1686, 

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; https://doi.org/10.21105/joss.01686.

Xie,Y. (2014) knitr: A Comprehensive Tool for Reproducible Research in R. In Victoria Stodden, Friedrich 

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; Leisch and Roger D. Peng, editors, Implementing Reproducible Computational Research. 

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; Chapman and Hall/CRC. ISBN 978-1466561595.
  
Xie,Y. (2015) Dynamic Documents with R and knitr. 2nd edition. Chapman and Hall/CRC.

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; ISBN 978-1498716963.

Xie,Y. (2020). knitr: A General-Purpose Package for Dynamic Report Generation in R. 

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; R package version 1.30.
